---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

you can use the ggplot2 function included in my package.

## Plot with examples

You can enable figure captions by `ggplot function` in package:

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r}
gp2007<-read.table(url("http://www.stat.umn.edu/geyer/3701/data/q1p4.txt"),header = TRUE)
ggplot2::ggplot(gp2007)+ggplot2::aes(x=x, y=p)+ggplot2::geom_point()
ggplot2::ggplot(gp2007)+ggplot2::aes(x=x, y=p)+ggplot2::geom_line()
ggplot2::ggplot(gp2007)+ggplot2::aes(x=x, y=p)+ggplot2::geom_area()
```

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

